%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size
\usepackage[colorlinks = true,
            linkcolor = gray,
            urlcolor  = gray,
            citecolor = gray,
            anchorcolor = gray]{hyperref}
 \usepackage[usenames,dvipsnames]{xcolor}



\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------
%no page numbering
\pagestyle{empty}
\begin{document}
\titlespacing{\section}{0pc}{1.5ex plus .1ex minus .2ex}{1pc}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Taras Murzenkov (Senior Software Engineer, Java/Kotlin) } % Print the main header

%------------------------------------------------

\parbox{0.2\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \>+34607046133\\ 
{\bf Email} \> \href{mailto:murzenkovtn@gmail.com}{murzenkovtn@gmail.com} % Mobile phone

\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
\\ % Email address
\\{\bf LinkedIn} \> \href{https://www.linkedin.com/in/tarasmurzenkov/}{https://www.linkedin.com/in/tarasmurzenkov/} % Mobile phone
\end{tabbing}}

%{
%\textbf{Languages:} Java 8-17, Kotlin, Groovy, SQL/HQL, JavaScript/TypeScript, Dart\newline
%\textbf{Frameworks/Libs:} Spring Boot, Quarkus, Hibernate ORM, jUnit, Testcontainers, Mockito, NodeJS/ExperssJS \newline
%\textbf{Databases:}  PostgreSQL, ElasticSearch, Cassandra, Redis \newline
%\textbf{Build tools:} Gradle, Maven \newline
%\textbf{Ops. tools:} Jenkins, Docker, Kubernetes, GitLab, Bash scripting, Terraform \newline
%\textbf{Queues:} Apache Kafka, RabbitMQ \newline
%\textbf{Clouds:} AWS, Digital Ocean, Heroku
%}
%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------
\section{Recent Experience}
\job
{Oct. 2022 }{ Current}
{Masabi}
{http://masabi.com}
{\textbf{Senior Software Engineer}}
{
\textbf{}   
\\$\bullet$ Architected and delivered a RESTful IoT provisioning service, enabling seamless device onboarding at scale.
\\$\bullet$ Implemented SSO authentication across identity providers streamlining user authentication.
\\$\bullet$ Designed RESTful APIs using OpenAPI specification so that customers were able to implement integration.
\\$\bullet$ Reduced critical API latency by 65\% through deep SQL query optimisation and strategic caching.
\\$\bullet$ Decreased AWS Lambda cold starts by 65\% by leveraging AWS SnapStart for faster execution.
\vadjust{\vspace{4pt}}
\newline
\textbf{Tech. stack: }{Kotlin, Java 17-21, Groovy, Python, Terraform, AWS (Lambda, DynamoDB, API Gateway, SQS, RDS), Apache Kafka, SpringBoot, http4k, Gradle, Maven, Cucumber, jUnit, WireMock, Testcontainers, GitLab, Bamboo}   
 }
 
 \job
{Nov. 2018 }{ Oct. 2022}
{Intellias}
{http://intellias.com}
{\textbf{Senior Software Engineer}}
{
\textbf{}   
\\$\bullet$ Designed and deployed two mission-critical event-driven web services to production, ensuring high scalability, reliability, and maintainability.
\\$\bullet$ Integrated a full end-to-end (E2E) testing pipeline into GitLab CI, boosting deployment frequency and system reliability.
\\$\bullet$ Developed and implemented a custom library to detect N+1 JPQL issues, cutting query latency by 70\% through advanced optimisation.
\\$\bullet$ Developed core libraries and embedded them into business-critical workflows to enhance accuracy and efficiency.
\vadjust{\vspace{4pt}}
\newline
\textbf{Tech. stack: }{Kotlin, Java 8-17, Terraform, Kubernetes, Docker, PostgreSQL, Redis, Apache Kafka, SpringBoot, Spring Reactor, Hibernate, Gradle, jUnit, WireMock, Testcontainers, Jenkins}   
 }

\job
{Oct. 2017}{Nov. 2018}
{EPAM}
{http://epam.ua/}
{\textbf{Software Software Engineer}}
{
\textbf{}    
\\$\bullet$ Reduced HTTP errors in legacy service communications by 50\% through the integration of reactive libraries
\\$\bullet$ Increased test coverage to 90\% and resolved SonarQube issues, ensuring compliance during a company audit
\\$\bullet$ Designed, load-tested, and optimized the data importing process, increasing throughput by 40\%
\\$\bullet$ Developed and integrated a service to fetch OFAC data, saving 5\% of employees’ daily time through process automation
\vadjust{\vspace{4pt}}
\newline
\textbf{Tech. stack: }{Java 8, Kubernetes, Docker, PostgreSQL, Redis, Apache Kafka, SpringBoot, Hibernate, Gradle, jUnit, WireMock, Jenkins, Sonar Qube}  
 }

\job
{Jun. 2015}{Oct. 2017}
{DataArt}
{http://dataart.ua/}
{\textbf{Software Engineer}}
{
\textbf{}  
\\$\bullet$ Developed a RESTful service that enabled financial analytics to scale the model design process, enhancing system performance
\\$\bullet$ Refactored Liquibase migration scripts to facilitate seamless database migration from Oracle to MS SQL Server
\\$\bullet$ Increased unit test coverage to 90\%, supporting the successful refactoring of the legacy codebase
\\$\bullet$ Integrated code quality metrics, reducing code complexity and improving the feature delivery process
\\$\bullet$ Planned and executed comprehensive load testing to assess the current system architecture and identify performance bottlenecks
\vadjust{\vspace{4pt}}
\newline

\textbf{Tech. stack: }{Java 7-8, SpringBoot, Hibernate, Apache POI, Oracle DB, Gradle, jUnit, WireMock, Jenkins, Sonar Qube}  
 }
 
 \section{Education}
 {
 \textbf{}  
 \\$\bullet$ MSc in "Financial management"  - \href{https://www.vlerick.com/en}{Vlerick Business School, Belgium, Ghent}
\\$\bullet$  MSc in Risk Management  - \href{https://www.hse.ru}{State University  Higher School of Economics}
\\$\bullet$  BS in Applied Mathematics and Statistics - \href{http://www.msu.ru/en/}{Lomonosov Moscow State University, Russia}
 }


\end{document}
 \usepackage{nopageno}